Measurement of ($\pi^-$-Ar) and ($K^+$-Ar) total hadronic cross sections in the LArIAT experiment

### 2018-05-29 Chapter-4/4-Methodology.tex
s

This chapter describes the general procedure employed to measure a total hadronic differential cross section in LArIAT.
Albeit with small differences, both the  ($\pi^{-}$,Ar) and (K$^{+}$,Ar) total hadronic cross section measurements rely on the same procedure. We start by selecting the particle of interest using a combination of beamline detectors and TPC information (Section \ref{ch:ParticleSelectionMethod}). We then perform a handshake between the beamline information and the TPC tracking to assure the selection of the correct TPC track (Section \ref{ch:WC2TPCMatchMethod}). Finally, we apply the ``thin slice" method and measure the ``raw" hadronic cross section (Section \ref{ch:ThinSliceMethod}). A series of corrections are then evaluated to obtain the ``true" cross section (Section \ref{ch:MCCorrections}).

At the end of this chapter, we show a sanity check of the methodology by applying the thin slice method employing only MC truth information and retrieving the Geant4 tabulated cross section for pions and kaons (Section \ref{ch:procedureTesting}).

\section{Event Selection}\label{ch:ParticleSelectionMethod}
The measurement of the ($\pi^{-}$,Ar) and (K$^{+}$,Ar) total hadronic cross section in LArIAT starts by selecting the pool of pion or kaon candidates and measuring their momentum.  This is done through the series of selections on  beamline and TPC information described in the next sections. The summary of the event selection in data is reported in Table \ref{tab:beamlineDataSelection}.

@@

\subsection{Selection of Beamline Events}\label{ch:beamlineDetectorsData}
As shown in equation \ref{eq:enFF}, we leverage the beamline particle identification and momentum measurement before entering the TPC as an input to evaluate the kinetic energy for the hadrons used in the  cross sections measurements. Thus, we select the LArIAT data to keep only events whose wire chamber and time of flight information is registered (line 1 in in Table \ref{tab:beamlineDataSelection}). Additionally, we perform a check of the plausibility of the trajectory inside the beamline detectors: given the position of the hits in the four wire chambers, we make sure the particle's trajectory does not cross any impenetrable material such as the collimator and the magnets steel (line 2 in in Table \ref{tab:beamlineDataSelection}).

@@

\subsection{TPC Selection: Halo Mitigation }\label{ch:pileUp}
The secondary beam impinging on LArIAT secondary target produces a plethora of particles which propagates downstream. The presence of upstream and downstream collimators greatly abates the number of particles tracing down the LArIAT tertiary beamline. However, it is possible that more than one particle sneaks into the LArTPC during its readout time: the TPC readout is triggered by the particle  firing the beamline detectors, but particles from the beam halo might be present in the TPC at the same time. We call ``pile up" the additional traces in the TPC. We adjusted the primary beam intensity between LArIAT Run I and Run II to reduce the presence of events with high pile up particles in the data sample. For the cross section analyses, we remove events with more than 4 tracks in the first 14 cm upstream portion of the TPC from the sample (line 5 in in Table \ref{tab:beamlineDataSelection}).

\subsection{TPC Selection: Shower Removal}\label{ch:electrons}
In the case of the ($\pi^-$,Ar) cross section, the resolution of  beamline mass spectrometer is not sufficient to select a beam of pure pions. In fact, muons and electrons survive the selection on the beamline mass. It is important to notice that the composition of the negative polarity beam is mostly pions, as will be discussed in section \ref{ch:beamlineComposition}.
Still, we devise a selection on the TPC information to mitigate the presence of electrons in the sample used for the pion cross section. The selection relies on the different topologies of a pion and an electron event in the argon: while the former will trace a track inside the TPC active volume, the latter will tend to ``shower", i.e. interact with the medium, producing bremsstrahlung photons which pair convert into several short tracks. In order to remove the shower topology, we create a region of interest (ROI) around the TPC track corresponding to the beamline particle. We look for short tracks contained in the ROI, as depicted in figure \ref{fig:showerFilt}:  if more then 5 tracks shorter than 10 cm are in the ROI, we reject the event. Line 7 in in Table \ref{tab:beamlineDataSelection} shows the number of events surviving this selection.

@@

\section{Beamline and TPC Handshake: the Wire Chamber to TPC Match}\label{ch:WC2TPCMatchMethod}
For each event passing the selection on its beamline information, we need to identify the track inside the TPC corresponding to the particle which triggered the beamline detectors, a procedure we refer to as ``WC to TPC match" (WC2TPC for short). In general, the TPC tracking algorithm will reconstruct more than one track in the event, partially due to the fact that hadrons interact in the chamber and partially because of pile up particles during the triggered TPC readout time, as shown in figure~\ref{fig:kaonInteraction}.

@@

We attempt to uniquely match one wire chamber track to one and only one reconstructed TPC track. 
In order to determine if a match is present, we apply a geometrical selection on the relative the position of the wire chamber and TPC tracks. 
We start by considering only TPC tracks whose first point is in the first 2 cm upstream portion of the TPC for the match.  We project the wire chamber track to the TPC front face where we define the coordinates of the projected point as  $x_{FF}$ and $y_{FF}$.  For each considered TPC track, we define $\Delta$X as the difference between the $x$ position of the most upstream point of the TPC track and $x_{FF}$.  $\Delta$Y is defined analogously. We define the radius difference, $\Delta$R, as $ \Delta \text{R} =  \sqrt{ \Delta \text{X}^2 +  \Delta \text{Y}^2}  $. We define  as $\alpha$ the angle between the incident WC track and the TPC track in the plane that contains them.  If  $\Delta \text{R} < 4 $~cm, $\alpha < 8^\circ $,  a match between WC-track and TPC track is found. We describe  how we determine the value for the radius and angular selection in Section \ref{ch:WC2TPCMatchOptimization}.
We discard events with multiple WC2TPC matches. We use only those TPC tracks that are matched to WC tracks in the cross section calculation. Line 6 in Table \ref{tab:beamlineDataSelection} shows the number of events where a unique WC2TPC match was found.

In MC, we mimic the matching between the WC and the TPC track by constructing a fake WC track using truth information at wire chamber four. We then apply the same WC to TPC matching algorithm as in data.

@@

\section{The Thin Slice Method}\label{ch:ThinSliceMethod}
Once we have selected the pool of hadron candidates and we have identified the TPC track corresponding to the beamline event, we apply the thin slice method to measure the cross section, as the following sections describe. 
\subsection{Cross Sections on Thin Target}
Cross section measurements on a thin target have been the bread and butter of nuclear and particle experimentalists since the Geiger-Marsden experiments \cite{Geiger1909}. At their core, this type of experiments consists in shooting a beam of particles with a known flux on a thin slab of material and recording the outgoing flux.

In general even in the case of thin target, the target is not a single particle, but rather a slab of material containing many diffusion centers. The so-called  ``thin target" approximation assumes that the target centers are uniformly distributed in the material and that the target is thin compared to the projectile interaction length, so that no center of interaction sits in front of another. In this approximation, the ratio between the number of particles interacting in the target $N_{\text{Int}}$ and the number of incident particles $N_{\text{Inc}}$ on the target determines the interaction probability $P_{Interacting}$, which is the complementary to one of the survival probability $P_{Survival}$. 
Equation \ref{eq:thinTargetXS} 
\begin{equation}
P_{Survival} = 1- P_{Interacting} = 1 - \frac{N_{\text{Int}}}{N_{\text{Inc}}} = e^{-\sigma_{TOT} n \delta X}
\label{eq:thinTargetXS}
\end{equation}
describes the probability for a particle to survive the thin target. This formula relates  the interaction probability to the total hadronic cross section ($\sigma_{TOT}$), the density of the target centers ($n$)\footnote{The scattering center density in the target, {\emph{n}},  relates to the argon density $\rho$, the Avogadro number  $ N_{A} $ and the argon molar mass $m_A$ as $n=\frac{\rho N_{A} }{m_A}$.}    and  the thickness of the target  along the incident hadron direction ($\delta X$). If the target is thin compared to the interaction length of the process considered, we can Taylor expand the exponential function in equation \ref{eq:thinTargetXS} and find a simple proportionality relationship between the cross section and the number of incident and interacting particles, as shown in equation \ref{eq:thinTargetXSTaylor}:
\begin{equation}
1 - \frac{N_{\text{Int}}}{N_{\text{Inc}}} =  1 -\sigma_{TOT} n \delta X + O(\delta X^2).
\label{eq:thinTargetXSTaylor}
\end{equation}

Solving for the cross section, we find:
\begin{equation}
 \sigma_{TOT}  = \frac{1}{n \delta X}\frac{N_{\text{Int}}}{N_{\text{Inc}}}.
\label{eq:thinTargetXSSolved}
\end{equation}

\subsection{Not-so-Thin Target: Slicing the Argon}\label{ch:XSRaw}
The interaction length of pions and kaons in argon is expected to be of the order of 50 cm for pions and 100 cm for kaons. Thus, the LArIAT TPC, with its 90 cm of length, is not a thin target. However, the fine-grained tracking of the LArIAT LArTPC allows us to treat the argon volume as a sequence of many adjacent thin targets.

As described in Chapter \ref{sec:experimentDescription}, LArIAT wire planes consist of 240 wires each. The wires are oriented at +/- $60^{\circ}$ from the vertical direction at 4 mm spacing, while the beam direction is oriented 3 degrees off the $z$ axis in the $XZ$ plane.  The wires collect signals proportional to the energy loss of the hadron along its path in a  $\delta${\emph{X}} = 4 mm/(sin($60^{\circ}$)cos($3^{\circ}$)) $\approx$ 4.7~mm slab of liquid argon. Thus, one can think to slice the TPC into many thin targets of $\delta${\emph{X}} = 4.7~mm thickness along the direction of the incident particle, making a measurement at each wire along the path.

@@

\begin{equation}
 E^{kin}_{Front Face}  = \sqrt{p^2_{Beam} - m^2_{Beam}} - m_{Beam} - E_{loss},
\label{eq:enFF}
\end{equation}
where $E_{loss}$ is a correction for the energy loss in the uninstrumented material between the beamline and the TPC front face. The  energy of the hadron at each slab is determined by subtracting the energy released by the particle in the previous slabs. For example, at the $j^{th}$ point of a track, the kinetic energy will be

@@

If the particle enters a slice, it contributes to $N_{\text{Inc}}( E^{kin})$ in the energy bin corresponding to its kinetic energy in that slice. If it interacts in the slice, it also contributes to $N_{\text{Int}}(E^{kin})$ in the appropriate energy bin. The cross section as a function of kinetic energy, $\sigma_{TOT}( E^{kin})$ will then be proportional to the ratio $\frac{N_{\text{Int}}( E^{kin})}{N_{\text{Inc}}( E^{kin})}$.

Our goal is to measure the total interaction cross section, independently  from the topology of the interaction. Thus, we determine that a hadron interacted simply by requiring that the last point of the WC2TPC matched track lies inside the fiducial volume, whose boundaries are defined in Table \ref{tab:FidVol}. If the TPC track stops within the fiducial volume, its last point will be the interaction point; if the track crosses the boundaries of the fiducial volume, the track will be considered ``through going" and no interaction point will be found. The only points of the hadronic candidate track considered to fill the  $N_{\text{Inc}})$ and  $N_{\text{Inc}}$ plots are the ones contained in the fiducial volume.

>>>>

This chapter describes the general procedure employed to measure  total hadronic interaction cross sections on Ar in LArIAT.
Albeit with small differences, both the  ($\pi^{-}$,Ar) and (K$^{+}$,Ar) total hadronic cross section measurements rely on the same procedure. We start by selecting the particle of interest using a combination of beamline detectors and TPC information (Section \ref{ch:ParticleSelectionMethod}). We then perform a handshake between the beamline information and the TPC tracking to assure the selection of the correct TPC track (Section \ref{ch:WC2TPCMatchMethod}) associated to the corresponding beam particle. We then apply the ``thin slice" method to measure the ``raw" hadronic cross section (Section \ref{ch:ThinSliceMethod}). A series of corrections are then evaluated and applied to obtain the final cross section (Section \ref{ch:MCCorrections}).

At the end of this chapter, we show a sanity check of the methodology by applying the thin slice method employing only MC truth information and retrieving the expected MC cross section for pions and kaons (Section \ref{ch:procedureTesting}).

\section{Event Selection}\label{ch:ParticleSelectionMethod}
The measurement of the ($\pi^{-}$,Ar) and (K$^{+}$,Ar) total hadronic cross section in LArIAT starts by selecting the pool of pion or kaon candidates and measuring their momentum before they enter the LAr volume.  This is done through the series of selections on  beamline and TPC information described in the next sections. The summary of the event selection in data is reported in Table \ref{tab:beamlineDataSelection}.

@@

\subsection{Selection of Beamline Events}\label{ch:beamlineDetectorsData}
We leverage the beamline particle identification and momentum measurement before entering the TPC as an input to evaluate the kinetic energy for the hadrons used in the  cross sections measurements. To this end, we select the LArIAT data to keep only events whose wire chamber and time of flight information is registered (line 1 in in Table \ref{tab:beamlineDataSelection}). Additionally, we perform a check of the plausibility of the trajectory inside the beamline detectors: given the position of the hits in the four wire chambers, we make sure the particle's trajectory does not cross any impenetrable material such as the collimator and the magnets steel (line 2 in in Table \ref{tab:beamlineDataSelection}).

@@

\subsection{TPC Selection: Halo Mitigation }\label{ch:pileUp}
The secondary beam impinging on LArIAT secondary target produces a plethora of particles which propagates downstream. The presence of upstream and downstream collimators greatly abates the number of particles tracing down the LArIAT tertiary beamline. However, it is possible that more than one particle sneaks into the LArTPC during its readout time: the TPC readout is triggered by the particle  firing the series of beamline detectors along our tertiary beamline, but particles from the beam halo might also be present in the TPC at the same time. We call ``pile up" the additional traces in the TPC. We adjusted the primary beam intensity between LArIAT Run I and Run II to reduce the presence of events with high pile up particles in the data sample. For the cross section analyses, we remove events with more than 4 tracks in the first 14 cm upstream portion of the TPC from the sample (line 5 in in Table \ref{tab:beamlineDataSelection}).

\subsection{TPC Selection: Shower Removal}\label{ch:electrons}
In the case of the ($\pi^-$,Ar) cross section, the resolution of  beamline mass spectrometer is not sufficient to select a beam of pure pions. In fact,  muons which are close in mass to the pions and relativistic electrons survive the selection on the beamline mass.  It is important to notice that the composition of the negative polarity beam is mostly pions, as will be discussed in section \ref{ch:beamlineComposition}.
Still, we devise a selection on the TPC information to mitigate the presence of electrons in the sample used for the pion cross section. The selection relies on the different topologies of a pion and an electron event when propagating in liquid argon: while the former will trace a track inside the TPC active volume, the latter will tend to ``shower", i.e. interact with the medium, producing bremsstrahlung photons which pair convert into several short tracks. In order to remove the shower topology, we create a region of interest (ROI) around the TPC track corresponding to the beamline particle. We look for short tracks contained in the ROI, as depicted in figure \ref{fig:showerFilt}:  if more then 5 tracks shorter than 10 cm are in the ROI, we reject the event. Line 7 in in Table \ref{tab:beamlineDataSelection} shows the number of events surviving this selection.

@@

\section{Beamline and TPC Handshake: the Wire Chamber to TPC Match}\label{ch:WC2TPCMatchMethod}
For each event passing the selection on its beamline information, we need to identify the track inside the TPC corresponding to the particle which triggered the beamline detectors, a procedure we refer to as ``WC to TPC match" (WC2TPC for short). In general, the TPC tracking algorithm can reconstruct more than one track in the event, partially due to the fact that hadrons interact in the chamber and partially because of pile up particles during the triggered TPC readout time, as shown in figure~\ref{fig:kaonInteraction}.

@@

We attempt to uniquely match one wire chamber track (see Section \ref{sec:MWPCfunc}) to one and only one reconstructed TPC track. 
In order to determine if a match is present, we apply a geometrical selection on the relative position of the wire chamber and TPC tracks. 
We start by considering only TPC tracks whose first point is in the first 2 cm upstream portion of the TPC for the match.  We project the wire chamber track to the TPC front face where we define the coordinates of the projected point as  $x_{FF}$ and $y_{FF}$.  For each considered TPC track, we define $\Delta$X as the difference between the $x$ position of the most upstream point of the TPC track and $x_{FF}$.  $\Delta$Y is defined analogously. We define the radius difference, $\Delta$R, as $ \Delta \text{R} =  \sqrt{ \Delta \text{X}^2 +  \Delta \text{Y}^2}  $. We define  as $\alpha$ the angle between the incident WC track and the TPC track in the plane that contains them.  If  $\Delta \text{R} < 4 $~cm, $\alpha < 8^\circ $,  a match between WC-track and TPC track is found. We describe  how we determine the value for the radius and angular selection in Section \ref{ch:WC2TPCMatchOptimization}.
We discard events with multiple WC2TPC matches. We use only those TPC tracks that are matched to WC tracks in the cross section calculation. Line 6 in Table \ref{tab:beamlineDataSelection} shows the number of events where a unique WC2TPC match was found.

In MC, we mimic the matching between the WC and the TPC track by constructing an artificial WC track using truth information at wire chamber four. We then apply the same WC to TPC matching algorithm as in data.

@@

\section{The Thin Slice Method}\label{ch:ThinSliceMethod}

Once we have selected the 40841 beamline pion candidates  and the 1081 beamline kaon candidates, and we have identified the TPC corresponding track, we apply the thin slice method to measure the cross section, as the following sections describe. 
\subsection{Cross Sections on Thin Target}
Cross section measurements on a thin target have been the bread and butter of nuclear and particle experimentalists since the Geiger-Marsden experiments \cite{Geiger1909}. At their core, this type of experiments consists in shooting a beam of particles with a known flux on a thin slab of material and recording the outgoing flux.

In general even in the case of thin target, the target is not a single particle, but rather a slab of material containing many diffusion centers. The so-called  ``thin target" approximation assumes that the target centers are uniformly distributed in the material and that the target is thin compared to the projectile interaction length, so that no center of interaction sits in front of another. In this approximation, the ratio between the number of particles interacting in the target $N_{\text{Int}}$ and the number of incident particles $N_{\text{Inc}}$ on the target estimates the interaction probability $P_{Interacting}$, which is the complementary to one of the survival probability $P_{Survival}$. 
Equation \ref{eq:thinTargetXS} 
\begin{equation}
P_{Survival} = 1- P_{Interacting} = 1 - \frac{N_{\text{Int}}}{N_{\text{Inc}}} = e^{-\sigma_{TOT}\text{ } n \text{ }\delta X}
\label{eq:thinTargetXS}
\end{equation}
describes the probability for a particle to survive the thin target. This formula relates  the interaction probability to the total hadronic cross section ($\sigma_{TOT}$), the density of the target centers ($n$)\footnote{The scattering center density in the target, {\emph{n}},  relates to the argon density $\rho$, the Avogadro number  $ N_{A} $ and the argon molar mass $m_A$ as $n=\frac{\rho N_{A} }{m_A}$.}    and  the thickness of the target  along the incident hadron direction ($\delta X$). If the target is thin compared to the interaction length of the process considered, we can Taylor expand the exponential function in equation \ref{eq:thinTargetXS} and find a simple proportionality relationship between the cross section and the number of incident and interacting particles, as shown in equation \ref{eq:thinTargetXSTaylor}:
\begin{equation}
1 - \frac{N_{\text{Int}}}{N_{\text{Inc}}} =  1 -\sigma_{TOT} \text{  }n \text{  }\delta X + O(\delta X^2).
\label{eq:thinTargetXSTaylor}
\end{equation}

Solving for the cross section, we find:
\begin{equation}
 \sigma_{TOT}  = \frac{1}{n \text{ }\delta X}\frac{N_{\text{Int}}}{N_{\text{Inc}}}.
\label{eq:thinTargetXSSolved}
\end{equation}

\subsection{Not-so-Thin Target: Slicing the Liquid Argon Volume}\label{ch:XSRaw}
The interaction length of pions and kaons in liquid argon is expected to be of the order of 50 cm for pions and 100 cm for kaons. Thus, the LArIAT TPC, with its 90 cm of length, is not a thin target. However, the fine-grained tracking of the LArIAT LArTPC allows us to treat the argon volume as a sequence of many adjacent thin targets.

As described in Chapter \ref{sec:experimentDescription}, LArIAT induction and collection planes consist of 240 wires each at 4 mm spacing. The wires are oriented at +/- $60^{\circ}$ from the vertical direction, while the beam direction is oriented 3 degrees off the $z$ axis in the $XZ$ plane.  The collection wires collect signals proportional to the energy deposited by the hadron along its path in a  $\delta${\emph{X}} = 4 mm/(sin($60^{\circ}$)cos($3^{\circ}$)) $\approx$ 4.7~mm slab of liquid argon. Thus, one can think to slice the TPC into many thin targets of $\delta${\emph{X}} = 4.7~mm thickness along the direction of the incident particle, making a measurement at each wire along the path.

@@

\begin{equation}
 E^{kin}_{Front Face}  = \sqrt{p^2_{Beam} - m^2_{Beam}} - m_{Beam} - E_{loss},
\label{eq:enFF}
\end{equation}
where $E_{loss}$ is a correction for the kinetic energy loss in the uninstrumented material between the beamline and the TPC front face. While propagating through the target,  the kinetic energy of the hadron at each slab is determined by subtracting the energy deposited by the particle in the previous slabs. For example, at the $j^{th}$ slab of a track, the kinetic energy will be

@@

If the particle enters a slice, it contributes to the $N_{\text{Inc}}( E^{kin})$ distribution in the energy bin corresponding to its kinetic energy in that slice. While into the slice, a hadron may or may not interact. If it interacts in the slice, it  contributes also to the $N_{\text{Int}}(E^{kin})$ distribution in the appropriate energy bin; this occurrence corresponds to the end of the hadron tracking. If the hadron does not interact, it will enter the next slice and the interaction evaluation starts again.
The process is applied to all the hadrons in the sample; the cross section as a function of kinetic energy, $\sigma_{TOT}( E^{kin})$ is then evaluated to be proportional to the ratio $\frac{N_{\text{Int}}( E^{kin})}{N_{\text{Inc}}( E^{kin})}$ -- bin by bin ratio.

Our goal is to measure the total interaction cross section, independently  from the topology of the interaction. Thus, we determine that a hadron interacted simply by requiring that the last point of the WC2TPC matched track lies in a slice within the fiducial volume, whose boundaries are defined in Table \ref{tab:FidVol}. If the TPC track ends within the fiducial volume, its last point will be the interaction point; if the track crosses the boundaries of the fiducial volume, the track will be considered ``through going" and no interaction point will be found. The only points of the hadronic candidate track considered to fill the  $N_{\text{Int}}$ and  $N_{\text{Inc}}$ distributions are the ones contained in the fiducial volume.
\textcolor{red}{ADD DECAY}

### 2018-05-29 thesis_main.tex
s

This thesis presents two world's first measurements: the measurement of ($\pi^-$-Ar) total hadronic cross section in the 100-1000 MeV kinetic energy range and the measurement of the ($K^+$-Ar) total hadronic cross section in the 100-600 MeV kinetic energy range. The analyses devised for these measurements use both the core elements of LArIAT: beamline and TPC. The first step in each analysis is the development of an event selection based on  beamline and TPC information geared towards the identification of the hadron of interest. We then proceed to match the beamline candidate to a suitable TPC track. Finally,  we apply the ``thin slice method" technique and measure the cross section, correcting for backgrounds and detector effects. The thin slice technique is a new method to measure hadron-argon cross sections possible only thanks to the combination of the tracking and calorimetry capability of the LArTPC technology. 
Albeit never on argon, the hadronic cross section of pions has been measured before on several different elements in thin target experiments, leading to solid predictions in the argon case. Even through the use of a different technique, our measurement of the  ($\pi^-$-Ar) total hadronic cross section is in general agreement with the prediction by the Geant4 Bertini Cascade model which are based on data from thin target experiments. On the contrary, cross section measurements for kaons are extremely rare, thus more difficult to model. Not surprisingly, our measurement of the  ($K^+$-Ar) total hadronic cross section is mostly in disagreement with the Geant4 prediction.

This thesis also reports two  ancillary  detector physics measurements necessary for the cross section analyses: the measurements of the LArIAT electric field and calorimetry constants. We developed a technique to measure the LArIAT electric field using cathode to anode piercing tracks with cosmic data. We applied a new technique for the measurement of the calorimetry calibration constants based on the particles' momentum measurement.

@@

% Starts proper arabic numbering of pages and chapters.
\input{Chapter-0/0-Introduction}
\mainmatter
\input{Chapter-1/1-Theory}
\input{Chapter-2/2-LArTPCs}
\input{Chapter-3/3-TheLArIATExperiment}
\input{Chapter-4/4-Methodology}
\input{Chapter-5/5-Preparatory}
\input{Chapter-6/6-PionCrossSection}
\input{Chapter-7/7-KaonCrossSection}
\input{Chapter-8/8-Conclusions}

%
%\input{Chapter-9/9-Uncertainty}

@@

%%\input{Chapters/C-MicroBooNECRT}

% Old chapters configuration %
%\input{Chapters/4-DataCollection}
%\input{Chapters/4-MonteCarlo}
%\input{Chapters/5-EnergyCalibration}
%\input{Chapter-8/8-TrackingOptimization}

>>>>

This thesis presents two world's first measurements: the measurement of ($\pi^-$-Ar) total hadronic cross section in the 100-1050 MeV kinetic energy range and the measurement of the ($K^+$-Ar) total hadronic cross section in the 100-650 MeV kinetic energy range. The analyses devised for these measurements use both the core elements of LArIAT: beamline and TPC. The first step in each analysis is the development of an event selection based on  beamline and TPC information geared towards the identification of the hadron of interest. We then proceed to match the beamline candidate to a suitable TPC track. Finally,  we apply the ``thin slice method" technique and measure the cross section, correcting for background and detector effects. The thin slice technique is a new method to measure hadron-argon cross sections possible only thanks to the combination of the tracking and calorimetry capability of the LArTPC technology. 
Albeit never on argon, the hadronic cross section of pions has been measured before on several different elements in thin target experiments, leading to solid predictions in the argon case. Through the use of a different technique, our measurement of the  ($\pi^-$-Ar) total hadronic cross section is in general agreement with the prediction by the Geant4 Bertini Cascade model which are based on data from thin target experiments. On the contrary, cross section measurements for kaons are extremely rare, thus more difficult to model. Not surprisingly, our measurement of the  ($K^+$-Ar) total hadronic cross section is mostly in disagreement with the Geant4 prediction.

This thesis also reports two  ancillary  detector physics measurements necessary for the cross section analyses: the measurements of the LArIAT electric field and calorimetry constants. We developed a technique to measure the LArIAT electric field using cathode-anode piercing tracks with cosmic data. We applied a new technique for the measurement of the calorimetry calibration constants based on the particles' momentum measurement.

@@

% Starts proper arabic numbering of pages and chapters.
\input{Chapter-0/0-Introduction}
\mainmatter
%\input{Chapter-1/1-Theory}
%\input{Chapter-2/2-LArTPCs}
%\input{Chapter-3/3-TheLArIATExperiment}
\input{Chapter-4/4-Methodology}
\input{Chapter-5/5-Preparatory}
\input{Chapter-6/6-PionCrossSection}
\input{Chapter-7/7-KaonCrossSection}
\input{Chapter-8/8-Conclusions}

@@
